When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2021-02-05 code/Tahkv1.Rmd
commit

  _This chapter explores variation in the professionalism of opinion pieces authored by retired US military officers and published in major US newspapers since 1979. Drawing on an original data set almost 400 opinion-editorial pieces published by retired military officers in The Wall Street Journal, The Washington Post, The New York Times, The Los Angeles Times, and the USA Today since 1979, the paper argues there has been an increase in published opinion pieces which fail to uphold the concept of military professionalism as defined by historical military norms and standards. What explains this variation? The author argues that increases in political polarization and the prestige of the military account for the increase in the number of op-eds which challenge traditional conceptions and norms of military professionalism. The paper concludes by arguing that the concept of "politicization of the military" --- something that previous civil-military relations scholars have identified and described --- must be widened to account not only for efforts by politicians to use the military for political advantages, but also for the phenomenon of retired military officers engaging the public to achieve political ends. The author argues that such a development, if uncorrected, will cause significant damage to the military as a profession._  
geometry: margin = 1.15in              # margin widths
fontsize: 12pt                         # text size
bibliography: researchpaper-ps904.bib # bibliography file
biblio-style: authoryear               # citation style
urlcolor: blue                         # links to external URLs
citecolor: black                       # links to bibliography
linkcolor: magenta                     # internal figures, footnotes, etc.
indent: true                          # paragraph format
                                       # true for indented paragraphs

@@

Using Gallup public opinion data, I include a measurement of the credibility of the American military as an institution. These surveys have asked Americans to rate the level of trust that they place in a variety of American institutions, such as the Presidency, Congress, Churches, and the Police. Since the late 1970s, the credibility of the American military as an institution has gradually increased [@gallup_polls_confidence_2020]. In 1979, 54% of those surveyed expressed either a great deal or quite a lot of confidence in the military, while in 2020, 72% expressed the same [@gallup_polls_confidence_2020]. Trends in political polarization (using DW-Nominate Scores and a measure of Affective Polarization) and confidence in the military are displayed in Figure Four, below.

>>>>

  _This chapter explores variation in the professionalism of opinion pieces authored by retired US military officers and published in major US newspapers since 1979. Drawing on an original data set of 390 opinion-editorial pieces published by retired military officers in The Wall Street Journal, The Washington Post, The New York Times, The Los Angeles Times, and the USA Today since 1979, the paper argues there has been an increase in published opinion pieces which fail to uphold the baseline norms of civil-military relations. This paper argues that this variation is the result of changes in two domestic political factors: political polarization and the overall prestige of the military institution. The paper concludes by arguing that the concept of "politicization of the military" --- something that previous civil-military relations scholars have identified and described --- must be widened to account not only for efforts by politicians to use the military for political advantages, but also for the phenomenon of retired military officers engaging the public to achieve political ends. The author argues that such a development, if uncorrected, will cause significant damage to the military as a profession._  
geometry: margin = 1.15in              # margin widths
fontsize: 12pt                         # text size
bibliography: researchpaper-ps904.bib # bibliography file
biblio-style: authoryear               # citation style
urlcolor: blue                         # links to external URLs
citecolor: black                       # links to bibliography
linkcolor: magenta                     # internal figures, footnotes, etc.
indent: true                          # paragraph format
                                       # true for indented paragraphs

@@

Using Gallup public opinion data, I include a measurement of the credibility of the American military as an institution. These surveys have asked Americans to rate the level of trust that they place in a variety of American institutions, such as the Presidency, Congress, Churches, and the Police. Since the late 1970s, the credibility of the American military as an institution has gradually increased [@noauthor_confidence_2020]. In 1979, 54% of those surveyed expressed either a great deal or quite a lot of confidence in the military, while in 2020, 72% expressed the same [@noauthor_confidence_2020]. Trends in political polarization (using DW-Nominate Scores and a measure of Affective Polarization) and confidence in the military are displayed in Figure Four, below.
